The JuliaHealth Observational Health Research Subecosystem

### 2024-01-01 paper.tex
Fixed up some more todos

% TODO::EASY Add link to code repository
\footnotetext{The code snippets presented in the body of the paper may omit certain intermediate steps. 
Please review the associated code repository for a full working tutorial.}

@@

% TODO::EASY Move this to a caption
A quick query of the cohort table (where the resulting subjects were stored) shows $\approx 1600$ from the dataset match this criteria.

@@

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|}
    \hline
        Race & Gender & Age Group & Cohort & Total & Prev. (\%) \\ \hline
        B/AA & F & 60 - 64 & 13 & 21 & 61.90 \\ \hline
        W & F & 50 - 54 & 59 & 111 & 53.15 \\ \hline
        W & F & 55 - 59 & 62 & 97 & 63.91 \\ \hline
        A & M & 80 - 84 & 6 & 10 & 60.00 \\ \hline
        UNK & F & 60 - 64 & 29 & 39 & 74.35 \\ \hline
        B/AA & M & 65 - 69 & 12 & 18 & 66.66 \\ \hline
    \end{tabular}
    % TODO::EASY Add a caption
    \caption{\textbf{Example of a Strep Throat Prevalence Calculation.} This illustrates the sort of results one can quickly generate using the OHS. Note, that although the prevalence values in this table are based on synthetic data and are not realistic, the output looks very similar to what one could expect to generate.}
    \label{table:eunomia_prevalence}
\end{table}

@@

% TODO::HARD Create table for MIMIC III results
% TODO::EASY Create reference to Eunomia table
As seen in Table 1, informative results can be rapidly generated by this workflow relevant to observational health research.
Although the values shown in Table 2 are synthetic and the crude prevalence values themselves are meaningless, we can take a this approach and apply it directly to the MIMIC III dataset.
In Table 3, we can calculate across this dataset meaningful statistics that could later be further analyzed and drive further questioning (such as ...).

>>>>

% TODO::EASY Add link to code repository
\footnotetext{The code snippets presented in the body of the paper may omit certain intermediate steps. 
Please review the associated code repository for a full working tutorial located here: https://github.com/TheCedarPrince/2022-JuliaCon-Proceedings-Submission}

@@

@@

\begin{table}[!ht]
    \centering
    \begin{tabular}{|l|l|l|l|l|l|}
    \hline
        Race & Gender & Age Group & Cohort & Total & Prev. (\%) \\ \hline
        B/AA & F & 60 - 64 & 13 & 21 & 61.90 \\ \hline
        W & F & 50 - 54 & 59 & 111 & 53.15 \\ \hline
        W & F & 55 - 59 & 62 & 97 & 63.91 \\ \hline
        A & M & 80 - 84 & 6 & 10 & 60.00 \\ \hline
        UNK & F & 60 - 64 & 29 & 39 & 74.35 \\ \hline
        B/AA & M & 65 - 69 & 12 & 18 & 66.66 \\ \hline
    \end{tabular}
    \caption{\textbf{Example of a Strep Throat Prevalence Calculation.} This illustrates the sort of results one can quickly generate using the OHS. Note, that although the prevalence values in this table are based on synthetic data and are not realistic, the output looks very similar to what one could expect to generate.}
    \label{table:eunomia_prevalence}
\end{table}

@@

% TODO::HARD Create table for MIMIC III results
As seen in \ref{table:eunomia_prevalence}, informative results can be rapidly generated by this workflow relevant to observational health research.
Although the values shown in Table 2 are synthetic and the crude prevalence values themselves are meaningless, we can take a this approach and apply it directly to the MIMIC III dataset.
In Table 3, we can calculate across this dataset meaningful statistics that could later be further analyzed and drive further questioning (such as ...).
